What is disputed on the web?

### 2010-02-01 papers/wicow_claimfinder/claimfinder.tex
Added cluster data

>>>>

\begin{figure}[tbh]
 \begin{center}
  \begin{tabular}{|lll|}
    \hline
    {\bf Noun} & {\bf Word Cluster} & {\bf Freq} \\
    \hline
   {\bf children} & tiger woods abused & 218\\
                  & instead encourage daily & 178\\
    \hline
   {\bf god} & daily encourage parents & 150 \\
   \hline
   {\bf government} & health care & 1267 \\
                    & united states & 427 \\
		    & relation environmental matters & 155 \\
   \hline
   {\bf iraq} & weapons mass destruction & 373 \\
              & united states & 247 \\
	      & saddam hussein & 192 \\
	      & al qaeda & 149 \\
   \hline
   {\bf israel} & middle east & 251 \\
		& allowed upon population & 128 \\
                & united states & 107 \\
		& off map & 106 \\
   \hline
   {\bf law}    & lawbreaker rather broken & 133 \\
		& united states &\\
   \hline
    {\bf obama} & working best interests & 568\\
                & health care & 481\\
	        & united states & 327 \\
		& nobel prize & 270 \\
		& legitimately president & 207 \\
		& ford hood shooter hasan nidal advised & 190 \\
		& birth certificate & 180\\
   \hline
   {\bf president} & united states & 439 \\
                   & health care & 203 \\
		   & george w & 164 \\
		   & aircraft system jolting bombing & 159 \\
		   & peace prize & 125 \\
		   & white house & 125 \\
   \hline
      {\bf war} & united states & 340 \\
   \hline

   {\bf women} & stay home & 183 \\
               & save vaccine & 85 \\
   \hline
  \end{tabular}
 \end{center}
 \label{cluster-figure}
 \caption{Largest word clusters found for nouns}
\end{figure}

\subsection{Clusters}
\label{clusters}

For each noun, we analysed the claims about that noun, and produced clusters that represent claims about that noun that seem to be particularly hotly disputed. Rather than clustering claims directly, we instead cluster together words that frequently co-occur. We used an agglomerative clustering algorithm, repeatedly merging the two clusters of words that had the most claims in common.
